Predicting sales of newly published books

### 2015-08-22 paper.tex
comentando los resultados obtenidos

In this research, the problem of how many books should be printed 
when a new book is published is faced using data provided by the 
Spanish publishing company Trevenque Editorial \footnote{{\tt http://editorial.trevenque.es}}.
The company's expert sales managers analized historical data 
and applied their knowledge using external variables to calculate
appropriate predictions, for example, increasing or decreasing the 
sales prediction based on season or sales period.
                        % varias citas - JJ
                        % [Pedro] lo modifico para comentar quienes nos facilitaron los datos
                        %  y que así era como funcionaban hasta ese momento.

@@

% Mean absolute error MAE / Root mean squared error RMSE /  Relative absolute error RAE / Root relative squared error RRSE
  % ¿Qué sentido tiene usar los 4 métodos de error? ¿Es que vamos a seleccionar uno? - JJ
  %[pedro] es lo habitual en los trabajos en los que se realizan tareas de predicción
  % en algunos calculan muchos más, pero estos son los más usados. 
Obtained results using the different forecasting methods on the dataset with 13 
variables per book can be shown in Table \ref{tabla:results13}:
\begin{table*}[!h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
 Method 	& Time (sec.) 	      & MAE 		& RMSE 		& RAE (\%) & RRSE (\%) 		\\
\hline
  MP5 		& 2.94 $\pm$ 0.51 	  & 65.49 	& 133.73 	& 11.10 	 & 9.17 	  \\
\hline
  LR 		  & 0.33 $\pm$ 0.07 	  & 100.813 & 257.63 	& 17.09 	 & 17.67 	\\
\hline
  SVM 		& 49.10 $\pm$ 8.05	  & 52.30	  & 139.45	& 8.87     & 9.56  	\\
\hline
  KNN 		& 0.03 $\pm$ 0.01 	  & 198.16 	& 542.93 	& 33.59 	 & 37.24 	\\
\hline
  MLP 		& 12.70 $\pm$ 3.08 	  & 97.18 $\pm$ 24.74 	& 174.77 $\pm$ 31.50 	& 16.47 $\pm$ 4.19 	& 11.99 $\pm$ 2.16 	\\
\hline
\end{tabular}
\end{center}
\caption{\small{Results (errors and time) obtained using the different
    forecasting methods on the dataset with 13 variables per book.}} 
\label{tabla:results13}
\end{table*}

  %[pedro] ya están los resultados de de tabla:results7 para MP5, LR, KNN, SVM.
  % faltan AUN algunas ejecuciones de los de MLP (actualizo con los resultados últimos media+-stdev)
Obtained results using the different forecasting methods on the dataset with 7 
variables per book can be shown in Table \ref{tabla:results7}:
\begin{table*}[!h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
 Method   & Time (sec.)         & MAE     & RMSE    & RAE (\%)  & RRSE (\%)      \\
\hline
  MP5     & 7.77 $\pm$ 1.15     & 117.78  & 260.05  & 18.51     & 17.00  \\
\hline
  LR      & 41.72 $\pm$ 8.41    & 120.29  & 252.91  & 18.91     & 16.54   \\
\hline
  SVM     & 1652.20 $\pm$ 283.50& 109.30  & 251.16   & 17.18    & 16.42   \\
\hline
  KNN     & 0.03 $\pm$ 0.01     & 293.98  & 1071.52  & 46.21    & 70.06   \\
\hline
  MLP     & 3646.76 $\pm$ 64.83 & 705.69 $\pm$ 77.22   & 1608.69 $\pm$ 42.96  & 110.92 $\pm$ 12.14   & 105.18 $\pm$ 2.81   \\
\hline
\end{tabular}
\end{center}
\caption{\small{Results (errors and time) obtained using the different 
forecasting methods on the dataset with 7 variables per book.}}
\label{tabla:results7}
\end{table*}

@@

M5P model obtained good results, both in time and error, and as stated before, 
this method can learn and tackle tasks with high dimensionality
and it generates reproducible and comprehensible representations that provide 
information on the decision process and does not require human intervention 
either for the operation or for interpretation. Thus, it is very suitable in 
order to be incorporated in a publishing company processes.

>>>>

In this research, the problem of how many books should be printed 
when a new book is published is faced using data provided by the 
Spanish publishing company Trevenque Editorial \footnote{{\tt http://editorial.trevenque.es}}.
The company's expert sales managers analyzed historical data 
and applied their knowledge using external variables to calculate
appropriate predictions, for example, increasing or decreasing the 
sales prediction based on season or sales period.
                        % varias citas - JJ
                        % [Pedro] lo modifico para comentar quienes nos facilitaron los datos
                        %  y que así era como funcionaban hasta ese momento.

@@

Table \ref{tabla:results13} shows obtained results (time to build the model and 
error) after applying the proposed forecasting methods on the dataset with 13 
variables per book.
In this dataset, every book is described using numerical variables, and thus, 
processing the data to build the different models is a fast task despite the 
number of instances.

% Mean absolute error MAE / Root mean squared error RMSE /  Relative absolute error RAE / Root relative squared error RRSE
  % ¿Qué sentido tiene usar los 4 métodos de error? ¿Es que vamos a seleccionar uno? - JJ
  %[pedro] es lo habitual en los trabajos en los que se realizan tareas de predicción
  % en algunos calculan muchos más, pero estos son los más usados. 
\begin{table*}[!h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
 Method 	& Time (sec.) 	      & MAE 		& RMSE 		& RAE (\%) & RRSE (\%) 		\\
\hline
  MP5 		& 2.94 $\pm$ 0.51 	  & 65.49 	& 133.73 	& 11.10 	 & 9.17 	  \\
\hline
  LR 		  & 0.33 $\pm$ 0.07 	  & 100.813 & 257.63 	& 17.09 	 & 17.67 	\\
\hline
  SVM 		& 49.10 $\pm$ 8.05	  & 52.30	  & 139.45	& 8.87     & 9.56  	\\
\hline
  KNN 		& 0.03 $\pm$ 0.01 	  & 198.16 	& 542.93 	& 33.59 	 & 37.24 	\\
\hline
  MLP 		& 12.70 $\pm$ 3.08 	  & 97.18 $\pm$ 24.74 	& 174.77 $\pm$ 31.50 	& 16.47 $\pm$ 4.19 	& 11.99 $\pm$ 2.16 	\\
\hline
\end{tabular}
\end{center}
\caption{\small{Results (errors and time) obtained using the different
    forecasting methods on the dataset with 13 variables per book.}} 
\label{tabla:results13}
\end{table*}

Obtained results (time to build the model and error) using the different 
forecasting methods on the dataset with 7 variables per book can be shown 
in Table \ref{tabla:results7}.
Although in this dataset each book is described using a smaller number of 
variables, two categorical variables, \emph{EDITORIAL} and \emph{MATTER}, are 
included, what that makes harder to process the instances and build the different 
models.

  %[pedro] ya están los resultados de de tabla:results7 para MP5, LR, KNN, SVM.
  % faltan AUN algunas ejecuciones de los de MLP (actualizo con los resultados últimos media+-stdev)
\begin{table*}[!h]
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline 
 Method   & Time (sec.)         & MAE     & RMSE    & RAE (\%)  & RRSE (\%)      \\
\hline
  MP5     & 7.77 $\pm$ 1.15     & 117.78  & 260.05  & 18.51     & 17.00  \\
\hline
  LR      & 41.72 $\pm$ 8.41    & 120.29  & 252.91  & 18.91     & 16.54   \\
\hline
  SVM     & 1652.20 $\pm$ 283.50& 109.30  & 251.16   & 17.18    & 16.42   \\
\hline
  KNN     & 0.03 $\pm$ 0.01     & 293.98  & 1071.52  & 46.21    & 70.06   \\
\hline
  MLP     & 3595.24 $\pm$ 97.50 & 691.84 $\pm$ 82.71   & 1619.92 $\pm$ 91.67  & 108.74 $\pm$ 13.00   & 105.91 $\pm$ 5.99   \\
\hline
\end{tabular}
\end{center}
\caption{\small{Results (errors and time) obtained using the different 
forecasting methods on the dataset with 7 variables per book.}}
\label{tabla:results7}
\end{table*}

% - indicar que el uso de las dos variables categóricas hace más difícil de aprender el conjunto
Paying attention to the obtained results shown in tables \ref{tabla:results13} 
and \ref{tabla:results7}, using those categorical variables as part of a big 
data set makes the problem hard to solve, both in required time to build the 
forecasting models as well as in the obtained errors.
However, as stated before, Trevenque expert sales manager, taking into account 
his knowledge in industry experience and their perceptions, decided that 
\emph{EDITORIAL} and \emph{MATTER} should taken into account.

@@

As far as the different methods is concerned, M5P model obtained good results, 
both in time and error, and as stated before, this method can learn and tackle 
tasks with high dimensionality and it generates reproducible and comprehensible 
representations that provide information on the decision process and does not 
require human intervention either for the operation or for interpretation. 
Thus, it is very suitable in order to be incorporated in a publishing company 
processes.
